Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of the Moran process for the Iterated Prisoner's Dilemma

### 2017-10-31 main.tex
Minor rephrasing of a sentence.

Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
good match (confirmed with a \(t\)-test in
Table~\ref{tab:comparison_stochastic}) which highlights the weakness of assuming
a given interaction between two IPD strategies can be summarised with a set of
utilities as shown in (\ref{equ:payoff_matrix}). For any given pair of
strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
given pair and can be quite a complex endeavour for stochastic strategies with
long memory: this is not necessary for the purposes of this work.  All data
generated for this validation exercise can be found at~\cite{data}.

>>>>

Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
good match (confirmed with a \(t\)-test in
Table~\ref{tab:comparison_stochastic}). This demonstrates that assuming
a given interaction between two IPD strategies can be summarised with a set of
utilities as shown in (\ref{equ:payoff_matrix}) is not correct. For any given pair of
strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
given pair and can be quite a complex endeavour for stochastic strategies with
long memory: this is not necessary for the purposes of this work.  All data
generated for this validation exercise can be found at~\cite{data}.
